\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-04-13 paper.tex
Added results for matlab opt

\begin{tablehere}
\centering
\begin{tabulary}{0.5\textwidth}{|C|C|C|C|C|}
\hline
       \# of Blades & Rotor Radius & Rotor Speed & \# of Rotors \\ \hline
  100 & 30 & 250 & 150 \\ \hline
\end{tabulary}
\caption{Optimal design variables}
\label{table:unbound_results}
\end{tablehere}

>>>>

\begin{tablehere}
\centering
\begin{tabulary}{0.5\textwidth}{|C|C|C|C|C|}
\hline
  \# of Blades & Rotor Radius & Rotor Speed & \# of Rotors \\ \hline
  3 & 2.306 & 39 & 8 \\ \hline
  Blade Pitch & Fuel Rate & Engine Size & Fuel Capacity \\ \hline
  22 & 2.01e-4 & 11.31 & 12.77 \\ \hline
\end{tabulary}
\caption{Optimal design variables for loosely bound constraints. Rotor radius is in meters, rotor speed is in RPM, blade pitch is in degrees, fuel rate is in kg/s, engine size is in cc, fuel capacity is in liters.}
\label{table:unbound_results}
\end{tablehere}
